HerMES: Spatially resolved ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-01-22 LaTeX/ms.tex
Alex Conley comments
Updated target names to be consistent with W13 and C14.

The quasars J0403$-$360, J2258$-$279, B0851$+$202, and J2258$-$279 were used
for bandpass and pointing calibration.  The quasars J0403$-$360, J0106$-$405,
J0519$-$454, J1008$+$063, and J0217$+017$ were used for amplitude and phase
gain calibration.  The following solar system objects were used for absolute
flux calibration: Callisto (CDFS targets), Neptune (XMM targets), Titan (COSMOS
targets) and Uranus (ADFS and XMM targets).  For ElaisS1, no solar system
object was observed.  Instead, J2258$-$279 was used for absolute flux
calibration, with the flux fixed according to a measurement made two days prior
to the observations of ElaisS1.

@@

In most targets, the peak of the SPIRE map is spatially coincident with the
location of the ALMA sources.  In one case where two ALMA sources are separated
by $\approx 10\arcsec$ (ADFS02), the elongation in the SPIRE 250$\,\mu$m map is
consistent with the angular separation of the two ALMA counterparts.
Otherwise, the SPIRE imaging is consistent with a single component located at
the centroid of the ALMA sources.  This result is not a surprise, given the
typical angular separation of the ALMA sources ($\lesssim 5\arcsec$) and the
FWHM of the SPIRE beam at 250$\,\mu$m (18.1$\arcsec$).

@@

Optical imaging observations using the Gemini Multi-Object Spectrograph-South
\citep[GMOS-S;][]{Hook:2004qy} were conducted in queue mode during the 2013B
semester as part of program GS-2013B-Q-77 (PI: R.~S.~Bussmann).  The goal of the
program is to use shallow $u$, $g$, $r$, $i$, and $z$ imaging to identify
structure at $z<1$ and determine which of the ALMA sources are affected by
gravitational lensing.  Nearly half of the ALMA sources lie in regions with
existing deep optical imaging thanks to the extensive HerMES multi-wavelength
dataset --- these were excluded from our Gemini-S program.  The remaining
targets are: ADFS01, ADFS02, ADFS03, ADFS04, ADFS05, ADFS06, ADFS07, ADFS\_M0,
ElaisS1, XMM02, XMM05, XMM101, XMM108, XMM109, and XMM115.  Each of these
targets were observed for a total of 9$\,$minutes of on-source integration time
in each of $u$, $g$, $r$, $i$, and $z$.  The observations were obtained during
dark time in with adequate seeing conditions (image quality $ = 85\% \approx
1.1\arcsec$.

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS01_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS03_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS04_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS05_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS06_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS07_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS_M0_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/CDFS_M0_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/CDFS_M1_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ECDFS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/COS01_870_250.pdf}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/COS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ElaisS1_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM01_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM03_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM04_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM05_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM06_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM16_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM101_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM102_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM108_870_250.pdf}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM109_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM110_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM115_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM119_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM124_870_250.pdf}
\end{centering}

@@

{\bf ADFS01:} Three sources are detected by ALMA, each of which is weakly
lensed by a bright foreground galaxy seen in the {\it HST} image.  Alternative
scenarios involving strong lensing can be ruled out by the location of the
lens: $\approx 2-3\arcsec$ north of the centroid of the ALMA sources (the rms
error in the astrometry is set from 2MASS at a level of $\approx 0\farcs4$) as
well as the unusual location and fluxes of the ALMA sources relative to each
other.  We assume an Einstein radius of $0\farcs5$ and fix the position angle
of the lens to be between 40-50 degrees to match the orientation seen in the
{\it HST} image.  Larger Einstein radii can be ruled out by the absence of
counter images north of the lens.

{\bf ADFS02:} Two sources are detected by ALMA, both of which are weakly lensed
by a foreground galaxy in the {\it HST} image.  The ALMA sources have the
largest separation of any in our sample overall: $\approx 10\arcsec$.  We
assume an Einstein radius of $1\farcs5$ for the foreground lens as a ``maximal
lensing'' scenario.  This results in magnification factors of $\mu_{870} = 2.3
\pm 0.1$ and $\mu_{870} = 1.2 \pm 0.1$ for the two sources.  Our constraints on
the true Einstein radius of the lens are weak, so these values for $\mu_{870}$
should be regarded as upper limits.

{\bf ADFS03:} Three sources are detected by ALMA, none of which appear to be
lensed (the closest bright {\it HST} source is located $\approx 13\arcsec$ away
from the ALMA sources).

{\bf ADFS04:} Three sources are detected by ALMA.  In this paper, we have
assumed that all three are unlensed.  There is a group of three sources
detected in our Gemini-S optical imaging located $\approx 7\arcsec$ east of the
ALMA sources.  This distance is so large that plausible mass ranges for the
Gemini-S sources would imply at most a factor of 1.1-1.2 boost in the apparent
flux densities of the ALMA sources.

{\bf ADFS05:} Two sources are detected by ALMA.  The nearest possible lens is
located $\approx 8\arcsec$ from the ALMA sources, indicating that lensing is
likely to be irrelevant in this system.  The two ALMA sources are similarly
bright ($S_{870} = 8.27 \pm 0.53\,$mJy and $S_{870} = 9.07 \pm 0.27\,$mJy) and
separated by $\approx 0\farcs8$, corresponding to a projected physical distance
of $\approx 6\,$kpc. This distance is typical of the pericentric passage
distance in both hydrodynamical simulations of major mergers
\citep[e.g.,][]{Hayward:2012lr} and CO observations of major mergers
\citep[e.g.,][]{2008ApJ...680..246T, 2010ApJ...724..233E, 2011ApJ...733L..11R,
2011MNRAS.412.1913I}.  Two plausible scenarios are that ADFS05 represents a
major merger that just experienced a first pass or is approaching final
coalescence, either of which significantly enhanced star-formation in the
system.

{\bf ADFS06:} Three sources are detected by ALMA, all of which are weakly
lensed by a foreground galaxy seen in the {\it HST} image.  We assume an
Einstein radius of $0\farcs5$ for the lens, as values larger than this produce
multiple images of the ALMA sources.  Based on the brightness of the lens, we
consider to be unlikely values for the Einstein radius that are smaller than
$0\farcs5$, so the results we report for this object should be robust.

{\bf ADFS07:} This is a single source that is strongly lensed by a foreground
galaxy seen in the {\it HST} image.  The lensed source is not detected by {\it
HST}.  The source is highly elongated ($q_s = 0.31 \pm 0.01$), but fits the
data very well.  The position of the lens according to the lens model is
consistent with the position in the {\it HST} image given the $0\farcs4$
fundamental uncertainty due to using the 2MASS system as the fundamental basis
for the astrometry.

{\bf ADFS\_M0:} Two sources are detected by ALMA, both of which are weakly
lensed by a group of small galaxies detected in the {\it HST} image.  We
represent the gravitational potential of the group with a single SIE lens and
an Einstein radius of $1\farcs0$.  Values larger than this produce additional
counter images that are not seen in the ALMA imaging.  We cannot rule out
smaller Einstein radii, but we consider these unlikely given the number of
sources and their brightness in the {\it HST} image.

{\bf CDFS\_M0:} This is a complex, very well constrained system.  Two sources
are detected by ALMA: one is strongly lensed and the other is weakly lensed.
In addition, the lens is detected by ALMA (this is one of two sources in the
entire ALMA sample that is unresolved by ALMA).  These facts work together to
provide very tight constraints on the system.  Since the lens is detected by
ALMA, its position relative to the lensed images is unambiguous.  Also, because
there is a strongly lensed source with multiple images, the Einstein radius of
the lens is unambiguous.  A byproduct of these two facts is that the
magnification factor of the weakly lensed source is known to very high
precision as well.  It experiences a magnification factor of $\mu_{870} =
1.520\pm0.002$ despite being located $\approx4\arcsec$ north of the lens (which
has an Einstein radius of $1.353\pm0.005$).  We use these numbers to inform our
estimates of the Einstein radius for weakly lensed sources without the
excellent contraints provided by this system.  Finally, this source is detected
(and unresolved) in the NRAO VLA Sky Survey \citep{Condon:1998uq}, having
$S_{\rm 1.4\,GHz} = 21.8 \pm 0.8\,$mJy.  Assuming all of this radio emission
originates from the lens, this implies a spectral slope of $\alpha = -0.24$ and
is consistent with non-thermal emission from the lens.

{\bf CDFS\_M1:} Two sources are detected by ALMA, both of which are weakly
lensed by a foreground galaxy seen in the {\it HST} image.  There is also a
3$\sigma$ peak coincident with {\it HST} source that may be an indication that
the lens has been detected by ALMA.  We do not attempt to model this 3$\sigma$
peak.  We assume an Einstein radius of $0\farcs5$ for the lens, since larger
values predict the existence of counter images that are not seen by ALMA.  The
second ALMA source is located $\approx5\arcsec$ from the lens and experiences a
small but significant magnification of $\mu_{870} = 1.12 \pm 0.02$.  Both ALMA
sources appear to be detected by IRAC and have similar mid-IR colors, suggesting
they lie at the same redshift (see Figure~\ref{fig:iraccolor}).

{\bf ECDFS02:} This system is very similar to ADFS05, except that here the two
ALMA sources are separated by $\approx 0\farcs4$ rather than $0\farcs8$ and one
source is brighter than the other by a factor of 2.  Assuming the two sources
have similar mass to light ratios, their brightness ratios indicate major
merger rather than minor merger activity.  The projected physical distance is
$\approx 2-3$kpc, assuming a redshift of $z=2$ for the ALMA sources.  This
could be an example of a major merger approaching final coalescence and
experiencing a significant boost in star-formation due to enhancements in the
local gas density brought about by tidal forces during the merger.

{\bf ElaisS1:} Four sources are detected by ALMA, all of which are weakly lensed
by a foreground galaxy seen in the {\it HST} image.  We assume an Einstein
radius of $1\farcs5$ for the lens as larger values begin to predict counter
images that are not seen by ALMA.  The magnification factors reported here
should be regarded as upper limits since we do not have strong constraints on
the lower limit of the Einstein radius of the lens (e.g., the magnication factor
for the source that is directly south of the lens is reported here to have
$\mu_{870} = 1.68 \pm 0.06$, but values as small as 1.1-1.2 are likely plausible
as well).  The ALMA sources are all detected by IRAC and their mid-IR colors are
similar, suggesting they lie at the same redshift (see
Figure~\ref{fig:iraccolor}).

{\bf COS01:} This system is similar to ADFS07: a single source that is strongly
lensed by a foreground galaxy seen in the {\it HST} image.  In fact, the
background source is also detected by {\it HST} as well as Keck/NIRC-II
adaptive optics imaging, and a lens model has been published based on these
data \citep{Calanog:2014lr}.  The morphology of the lensed emission is very
different between the Keck and ALMA imaging, suggesting differential
magnification is important in this object.  The very small sizes of the sources
are consistent with this as well ($r_s = 0.023 \pm 0.003\arcsec$, Keck and $r_s
= 0.055 \pm 0.007\arcsec$, ALMA).  Adopting a redshift of $z=2$ for the lensed
source implies physical sizes of $\approx 150\,$pc and $\approx 300\,$pc for
the rest-frame optical and rest-frame FIR, respectively.

{\bf COS02:} Five sources are detected by ALMA \citep[the brightest of which has
already been detected;][]{Smolcic:2012zl}, none of which appear to be lensed.
Previous research has shown this to be an overdense region \citep[this object is
called COSBO3 in][]{Aravena:2010fr} with a photometric redshift of $z=2.3-2.4$.
Our ALMA imaging offers the first convincing evidence that the associated
galaxies in the overdensity are sub-mm bright and thus intensely star-forming.
There are a number of $2-3\sigma$ peaks in the map that could be real.  This
would further increase the multiplicity rate for this object, but we caution
that there are also negative peaks of similar amplitude (i.e., $2-3\sigma$)
present in this map.  Some of the ALMA sources have counterparts detected in the
{\it HST} image, whereas all of the ALMA sources are detected by IRAC (see
Figure~\ref{fig:iraccolor}).  Their mid-IR colors are similar, providing further
evidence that the ALMA sources lie at the same redshift.

{\bf XMM01:} Three sources are detected by ALMA, all of which are weakly lensed
by two foreground galaxies seen in the {\it HST} and Keck/NIRC-II imaging.  The
ALMA imaging is broadly consistent with SMA data originally presented in
\citet{Fu:2013lr}, with two bright sources and a much fainter third source very
close to the more southern bright source.  We assume Einstein radii of
$0\farcs5$ for both lenses to reproduce the approach used in \citet{Fu:2013lr}.
This results in magnification factors for the three sources of $\mu_{870}
\approx 1.6 - 1.7$, similar to \citet{Fu:2013lr}.

{\bf XMM02:} Two sources are detected by ALMA, both of which are weakly lensed.
This system is similar to ADFS02, although the two ALMA sources are much closer
and the lens must be less massive in order to avoid producing multiple images
of the closest ALMA source.  The fainter ALMA source has a much lower
magnification factor than the brighter source ($\mu_{870} = 1.10 \pm 0.01$ vs.
$\mu_{870} = 1.63 \pm 0.11$).  As with ADFS02, we caution that these
magnification factors represent the ``maximal lensing'' scenario and hence
should be considered upper limits.  Both ALMA sources are detected by IRAC and
have similar mid-IR colors, suggesting they lie at a similar redshift (see
Figure~\ref{fig:iraccolor}).

{\bf XMM03:} One source is detected by ALMA, and it is weakly lensed by two
foreground galaxies seen in the {\it HST} images.  We assume an Einstein radius
of 1$\arcsec$ for the foreground lenses and fix the positions of both lenses
according to the location of the foreground galaxies in the {\it HST} image.
As with XMM02, this is the ``maximal lensing'' scenario, so our magnification
measurement of $\mu_{870} = 1.80 \pm 0.16$ should be considered an upper limit.

{\bf XMM04:} Two sources are detected by ALMA, none of which appear to be
lensed.  The brighter ALMA source is weakly detected in the CFHT $i$-band
image.

{\bf XMM05:} One source is detected by ALMA, and it is weakly lensed by a group
of foreground galaxies seen in the {\it HST} image.  We assume an Einstein
radius of $0\farcs2$ for the nearest lensing galaxy and allow a $\pm0\farcs4$
shift in its position relative to that indicated by the {\it HST} image (which
has its astrometry tied to SDSS).  We represent the remaining members of the
group as a single SIS located $4\farcs5$ south and $4\farcs5$ east of the image
centroid and having an Einstein radius of $2\farcs0$.  This is meant to
represent the ``maximal lensing'' scenario, so our measurement of $\mu_{870}$
should be regarded as an upper limit.  The presence of two $3\sigma$ peaks
located near the center of the residual image indicates that the model does not
fit the data perfectly.  This could be an indication that either of our
assumptions for the lens potential or source structure are oversimplifications.
Higher resolution imaging is needed to determine the most likely cause.

{\bf XMM06:} One source is detected by ALMA, and it is strongly lensed by one
foreground galaxy seen in the {\it HST} image.  The lensed source is not
detected in the {\it HST} image.  This object also has high quality SMA imaging
and an accompanying lens model that produces consistent results with those
given here \citep{Bussmann:2013lr}.

>>>>

The quasars J0403$-$360, J2258$-$279, B0851$+$202, and J2258$-$279 were used
for bandpass and pointing calibration.  The quasars J0403$-$360, J0106$-$405,
J0519$-$454, J1008$+$063, and J0217$+017$ were used for amplitude and phase
gain calibration.  The following solar system objects were used for absolute
flux calibration: Callisto (CDFS targets), Neptune (XMM targets), Titan (COSMOS
targets) and Uranus (ADFS and XMM targets).  For HELAISS02, no solar system
object was observed.  Instead, J2258$-$279 was used for absolute flux
calibration, with the flux fixed according to a measurement made two days prior
to the observations of HELAISS02.

@@

In most targets, the peak of the SPIRE map is spatially coincident with the
location of the ALMA sources.  In one case where two ALMA sources are separated
by $\approx 10\arcsec$ (HADFS08), the elongation in the SPIRE 250$\,\mu$m map is
consistent with the angular separation of the two ALMA counterparts.
Otherwise, the SPIRE imaging is consistent with a single component located at
the centroid of the ALMA sources.  This result is not a surprise, given the
typical angular separation of the ALMA sources ($\lesssim 5\arcsec$) and the
FWHM of the SPIRE beam at 250$\,\mu$m (18.1$\arcsec$).

@@

Optical imaging observations using the Gemini Multi-Object Spectrograph-South
\citep[GMOS-S;][]{Hook:2004qy} were conducted in queue mode during the 2013B
semester as part of program GS-2013B-Q-77 (PI: R.~S.~Bussmann).  The goal of the
program is to use shallow $u$, $g$, $r$, $i$, and $z$ imaging to identify
structure at $z<1$ and determine which of the ALMA sources are affected by
gravitational lensing.  Nearly half of the ALMA sources lie in regions with
existing deep optical imaging thanks to the extensive HerMES multi-wavelength
dataset --- these were excluded from our Gemini-S program.  The remaining
targets are: HADFS03, HADFS08, HADFS09, HADFS10, HADFS02, HADFS04, HADFS01, HADFS11,
HELAISS02, HXMM11, HXMM12, HXMM22, HXMM07, HXMM30, and HXMM04.  Each of these
targets were observed for a total of 9$\,$minutes of on-source integration time
in each of $u$, $g$, $r$, $i$, and $z$.  The observations were obtained during
dark time in with adequate seeing conditions (image quality $ = 85\% \approx
1.1\arcsec$.

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HELAISS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM31_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM29_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM07_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM20_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM01_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM04_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM09_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM03_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM11_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM23_870_250.pdf}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM22_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM05_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM30_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM12_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HECDFS12_870_500.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HECDFS04_870_500.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HECDFS13_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS04_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS11_870_500.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS10_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS01_870_250.pdf}
\end{centering}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS09_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS08_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS03_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HCOSMOS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/HCOSMOS01_870_250.pdf}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\end{centering}

@@

{\bf HELAISS02:} Four sources are detected by ALMA, all of which are weakly
lensed by a foreground galaxy seen in the {\it HST} image.  We assume an
Einstein radius of $1\farcs5$ for the lens as larger values begin to predict
counter images that are not seen by ALMA.  The magnification factors reported
here should be regarded as upper limits since we do not have strong constraints
on the lower limit of the Einstein radius of the lens (e.g., the magnication
factor for the source that is directly south of the lens is reported here to
have $\mu_{870} = 1.68 \pm 0.06$, but values as small as 1.1-1.2 are likely
plausible as well).  The ALMA sources are all detected by IRAC and their mid-IR
colors are similar, suggesting they lie at the same redshift (see
Figure~\ref{fig:iraccolor}).

{\bf HXMM02:} One source is detected by ALMA, and it is strongly lensed by one
foreground galaxy seen in the {\it HST} image.  The lensed source is not
detected in the {\it HST} image.  This object also has high quality SMA imaging
and an accompanying lens model that produces consistent results with those
given here \citep{Bussmann:2013lr}.

{\bf HXMM31:} Two sources are detected by ALMA, neither of which are lensed.
The faint, diffuse emission seen in the CFHT $i$-band image is atypical of
lensing galaxies.  The nearest bright galaxy seen at $i$-band is located
$\approx 18\arcsec$ southeast of the ALMA sources.

{\bf HXMM29:} Two sources are detected by ALMA, none of which appear to be
lensed.  The brighter ALMA source is weakly detected in the CFHT $i$-band
image.

{\bf HXMM07:} One source is detected by ALMA, and it is strongly lensed by one
foreground galaxy detected in the Gemini-S image.  There is a $\approx
0\farcs5$ offset in the position of the foreground galaxy between the lens
model and the Gemini-S image.  Given the absolute astrometric uncertainty of
$0\farcs2$ (based on SDSS), we do not consider this offset to be significant.
The presence of a handful of $\pm3\sigma$ peaks in the residual map is likely
an indication that our assumption of a single Gaussian to describe the source
morphology is an oversimplification.

{\bf HXMM20:} Five sources are detected by ALMA, none of which appear to be
lensed.  There are a few faint smudges seen in the {\it HST} image which are
likely to be the rest-frame optical counterparts to the ALMA sources.  The ALMA
sources are all arranged in a chain like shape, possibly suggestive of a larger
filamentary overdensity in which they might reside.  IRAC imaging provides
support for this hypothesis (see Figure~\ref{fig:iraccolor}), as all of the ALMA
sources are detected and have similar mid-IR colors (suggesting they lie at
similar redshift).

{\bf HXMM01:} Three sources are detected by ALMA, all of which are weakly lensed
by two foreground galaxies seen in the {\it HST} and Keck/NIRC-II imaging.  The
ALMA imaging is broadly consistent with SMA data originally presented in
\citet{Fu:2013lr}, with two bright sources and a much fainter third source very
close to the more southern bright source.  We assume Einstein radii of
$0\farcs5$ for both lenses to reproduce the approach used in \citet{Fu:2013lr}.
This results in magnification factors for the three sources of $\mu_{870}
\approx 1.6 - 1.7$, similar to \citet{Fu:2013lr}.

{\bf HXMM04:} One source is detected by ALMA, and it is weakly lensed by a
foreground galaxy seen in the {\it HST} image.  We assume an Einstein radius of
$0\farcs5$ to represent the ``maximal lensing'' scenario.  Due to the
elliptical nature of the lens, this results in a magnification factor of
$\mu_{870} = 3.72 \pm 0.42$.  The {\it HST} morphology is complex: diffuse
emission to the north of the lens could be a detection of the background source
or could be a long spiral arm associated with the lensing galaxy.

{\bf HXMM09:} Two sources are detected by ALMA, both of which are weakly
lensed by a foreground galaxy detected in the {\it HST} image.  An Einstein
radius of $1\farcs5$ is used to represent the ``maximal lensing'' scenario and
results in magnification factors of $\mu_{870} = 2.25 \pm 0.17$ and $\mu_{870}
= 1.48 \pm 0.09$.

{\bf HXMM03:} Three sources are detected by ALMA, all of which are weakly lensed
by a foreground galaxy detected in the {\it HST} image and located $\approx
6\arcsec$ from the ALMA sources.  The central source is much brighter than the
other two sources, which makes fitting a model challenging.  We forced the
positions of the second and third sources to be at least $0\farcs5$ and
$-0\farcs5$ away from the first source in declination, respectively.
Furthermore, we fixed the position of the lens to be located $2\farcs5$ west
and $0\farcs5$ south of the image centroid given in Table~\ref{tab:position}.
We also fixed the Einstein radius to be $1\farcs0$, a typical value for
isolated galaxies in this sample and in \citet{Bussmann:2013lr}.  Because the
source is so far from the lens, the magnification factor is only $\mu_{870} =
1.19 \pm 0.01$.

{\bf HXMM11:} Two sources are detected by ALMA, both of which are weakly lensed.
This system is similar to HADFS08, although the two ALMA sources are much closer
and the lens must be less massive in order to avoid producing multiple images
of the closest ALMA source.  The fainter ALMA source has a much lower
magnification factor than the brighter source ($\mu_{870} = 1.10 \pm 0.01$ vs.
$\mu_{870} = 1.63 \pm 0.11$).  As with HADFS08, we caution that these
magnification factors represent the ``maximal lensing'' scenario and hence
should be considered upper limits.  Both ALMA sources are detected by IRAC and
have similar mid-IR colors, suggesting they lie at a similar redshift (see
Figure~\ref{fig:iraccolor}).

{\bf HXMM23:} One source is detected by ALMA, and it is coincident (within the
astrometric uncertainty) with a late-type galaxy seen in the {\it HST} image.
Here, we assume that the {\it HST} source is the true counterpart to the ALMA
source, implying that no lensing is occuring.  Consistent with this hypothesis
is that the SPIRE photometry show blue colors that suggest this object is at low
redshift.

{\bf HXMM22:} One source is detected by ALMA, and it appears to be unlensed.  A
faint smudge seen in the {\it HST} image of this source is due to a star
located $3\farcs5$ northeast of the ALMA source.

{\bf HXMM05:} One source is detected by ALMA, and it is weakly lensed by two
foreground galaxies seen in the {\it HST} images.  We assume an Einstein radius
of 1$\arcsec$ for the foreground lenses and fix the positions of both lenses
according to the location of the foreground galaxies in the {\it HST} image.
As with HXMM11, this is the ``maximal lensing'' scenario, so our magnification
measurement of $\mu_{870} = 1.80 \pm 0.16$ should be considered an upper limit.

{\bf HXMM30:} One source is detected by ALMA, and it is strongly lensed by one
foreground galaxy detected in the Gemini-S image.  As with HXMM07, there is a
$\approx 0\farcs5$ offset between the lens position according to the lens model
and the Gemini-S image.  We do not consider this offset significant.  An
alternative model in which the lens is sub-mm luminous cannot be ruled out, but
we consider this unlikely for a number of reasons.  First, it is a more complex
model (having two sources and one lens, rather than one source and one lens).
Second, lenses are very rarely detected in sub-mm imaging.  Third, the shape
and location of the ALMA sources relative to the Gemini-S source are typical of
strongly lensed objects (consistent with the very low residuals).  Fourth, the
alternative lens model predicts the lensed source to have an intrinsic flux
density of $\approx 13 \,$mJy, which would make it the brightest source in the
sample.

{\bf HXMM12:} One source is detected by ALMA, and it is weakly lensed by a group
of foreground galaxies seen in the {\it HST} image.  We assume an Einstein
radius of $0\farcs2$ for the nearest lensing galaxy and allow a $\pm0\farcs4$
shift in its position relative to that indicated by the {\it HST} image (which
has its astrometry tied to SDSS).  We represent the remaining members of the
group as a single SIS located $4\farcs5$ south and $4\farcs5$ east of the image
centroid and having an Einstein radius of $2\farcs0$.  This is meant to
represent the ``maximal lensing'' scenario, so our measurement of $\mu_{870}$
should be regarded as an upper limit.  The presence of two $3\sigma$ peaks
located near the center of the residual image indicates that the model does not
fit the data perfectly.  This could be an indication that either of our
assumptions for the lens potential or source structure are oversimplifications.
Higher resolution imaging is needed to determine the most likely cause.

{\bf HECDFS12:} This is a complex, very well constrained system.  Two sources
are detected by ALMA: one is strongly lensed and the other is weakly lensed.
In addition, the lens is detected by ALMA (this is one of two sources in the
entire ALMA sample that is unresolved by ALMA).  These facts work together to
provide very tight constraints on the system.  Since the lens is detected by
ALMA, its position relative to the lensed images is unambiguous.  Also, because
there is a strongly lensed source with multiple images, the Einstein radius of
the lens is unambiguous.  A byproduct of these two facts is that the
magnification factor of the weakly lensed source is known to very high
precision as well.  It experiences a magnification factor of $\mu_{870} =
1.520\pm0.002$ despite being located $\approx4\arcsec$ north of the lens (which
has an Einstein radius of $1.353\pm0.005$).  We use these numbers to inform our
estimates of the Einstein radius for weakly lensed sources without the
excellent contraints provided by this system.  Finally, this source is detected
(and unresolved) in the NRAO VLA Sky Survey \citep{Condon:1998uq}, having
$S_{\rm 1.4\,GHz} = 21.8 \pm 0.8\,$mJy.  Assuming all of this radio emission
originates from the lens, this implies a spectral slope of $\alpha = -0.24$ and
is consistent with non-thermal emission from the lens.

{\bf HECDFS04:} Two sources are detected by ALMA, both of which are weakly
lensed by a foreground galaxy seen in the {\it HST} image.  There is also a
3$\sigma$ peak coincident with {\it HST} source that may be an indication that
the lens has been detected by ALMA.  We do not attempt to model this 3$\sigma$
peak.  We assume an Einstein radius of $0\farcs5$ for the lens, since larger
values predict the existence of counter images that are not seen by ALMA.  The
second ALMA source is located $\approx5\arcsec$ from the lens and experiences a
small but significant magnification of $\mu_{870} = 1.12 \pm 0.02$.  Both ALMA
sources appear to be detected by IRAC and have similar mid-IR colors, suggesting
they lie at the same redshift (see Figure~\ref{fig:iraccolor}).

{\bf HECDFS13:} This system is very similar to HADFS02, except that here the two
ALMA sources are separated by $\approx 0\farcs4$ rather than $0\farcs8$ and one
source is brighter than the other by a factor of 2.  Assuming the two sources
have similar mass to light ratios, their brightness ratios indicate major
merger rather than minor merger activity.  The projected physical distance is
$\approx 2-3$kpc, assuming a redshift of $z=2$ for the ALMA sources.  This
could be an example of a major merger approaching final coalescence and
experiencing a significant boost in star-formation due to enhancements in the
local gas density brought about by tidal forces during the merger.

{\bf HADFS04:} Three sources are detected by ALMA, all of which are weakly
lensed by a foreground galaxy seen in the {\it HST} image.  We assume an
Einstein radius of $0\farcs5$ for the lens, as values larger than this produce
multiple images of the ALMA sources.  Based on the brightness of the lens, we
consider to be unlikely values for the Einstein radius that are smaller than
$0\farcs5$, so the results we report for this object should be robust.

{\bf HADFS02:} Two sources are detected by ALMA.  The nearest possible lens is
located $\approx 8\arcsec$ from the ALMA sources, indicating that lensing is
likely to be irrelevant in this system.  The two ALMA sources are similarly
bright ($S_{870} = 8.27 \pm 0.53\,$mJy and $S_{870} = 9.07 \pm 0.27\,$mJy) and
separated by $\approx 0\farcs8$, corresponding to a projected physical distance
of $\approx 6\,$kpc. This distance is typical of the pericentric passage
distance in both hydrodynamical simulations of major mergers
\citep[e.g.,][]{Hayward:2012lr} and CO observations of major mergers
\citep[e.g.,][]{2008ApJ...680..246T, 2010ApJ...724..233E, 2011ApJ...733L..11R,
2011MNRAS.412.1913I}.  Two plausible scenarios are that HADFS02 represents a
major merger that just experienced a first pass or is approaching final
coalescence, either of which significantly enhanced star-formation in the
system.
